Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
change order of words

The idea of cluster analysis, which originated in the 1930s in the anthropology field [@driver1932, @zubin1938], is to group objects with similar characteristics.
In the spatial context, the similarity of spatial coordinates is used to form such groups.
Different cluster algorithms such as hierarchical, density-based, grid-based or centroid-based clustering exist [@gower1967].

>>>>

The idea of cluster analysis, which originated in the 1930s in the field of anthropology [@driver1932, @zubin1938], is to group objects with similar characteristics.
In the spatial context, the similarity of spatial coordinates is used to form such groups.
Different cluster algorithms such as hierarchical, density-based, grid-based or centroid-based clustering exist [@gower1967].
